%\documentclass[12pt,a4paper,BCOR15mm,twoside,DIV12]{article}
\documentclass{article}
\usepackage[paper=a4paper,left=20mm,right=20mm,top=25mm,bottom=25mm]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{color}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{makeidx}
\usepackage{graphicx, float,epsfig}
\usepackage[nottoc,numbib]{tocbibind}


\newcommand{\properideal}{%
  \mathrel{\ooalign{$\lneq$\cr\raise.22ex\hbox{$\lhd$}\cr}}}

\def\P{\mathcal{P}}
\def\I{\mathbb{I}}
\def\R{\mathbb{R}} 
\def\E{\mathcal{E}} 
\def\NE{\mathbb{N}_{\geq1}} 
\def\N{\mathbb{N}} 
\def\Z{\mathbb{Z}} 
\def\Q{\mathbb{Q}} 
\def\F{\mathbb{F}}
\def\Vm{\mathcal{V}_m}
\def\V{\mathcal{V}}
\def\VV{\mathbb{V}}
\def\C{\mathbb{C}}
\def\U{\mathcal{U}}
\def\a{\mathfrak{a}}
\def\b{\mathfrak{b}}
\def\p{\mathfrak{p}}
\def\q{\mathfrak{q}}
\def\s{\sigma}
\def\si{\unlhd_{\sigma}}
\def\GL{\text{GL}}
\def\supp{\text{Supp}}
\def\id{\text{id}}
\def\n{\underline{n}}
\def\Spec{\text{Spec}}
\def\sSpec{\sigma\text{-Spec}}
\def\diag{\text{diag}}
\def\End{\text{End}}
\def\Hom{\text{Hom}}
\def\fa{\text{ for all }}
\def\Tr{\text{Tr}}
\def\Id{\text{Id}}
\def\Sym{\text{Sym}}
\def\H{\mathcal{H}}
\def\wt{\text{wt}}
\def\Perf{\text{Perf}}


\renewcommand{\labelenumi}{\alph{enumi})}
%\renewcommand{\P}{\textfrak{P}}
\newcommand{\cupdot}{\mathop{\mathaccent\cdot\cup}}
\newcommand{\textsim}{\mathord{\sim}}
\newenvironment{bew}{\begin{proof}[Proof]}{\end{proof}}
\theoremstyle{plain}
\newtheorem{Satz}{Satz}[section]
\newtheorem{theorem}[Satz]{Theorem}
\newtheorem{ex}[Satz]{Example}
\newtheorem{cor}[Satz]{Corollary}
\newtheorem{algorithm}[Satz]{Algorithm}
\newtheorem{prop}[Satz]{Proposition}
\newtheorem{lem}[Satz]{Lemma}
\newtheorem{defn}[Satz]{Definition}
\theoremstyle{definition}
\newtheorem{rem}[Satz]{Remark}


\makeindex
\title{Mixed Ideals in Difference Algebra}
\author{Andr\'{e}s Goens}
\date{\today}
\begin{document}
\setlength{\parindent}{1.5em}
\section{An alternative proof of the theorem about the decomposition of radical, mixed $\s$-ideals in prime $\s$-ideals}
\begin{defn}
Let $R$ be a difference ring and $\a \si R$ be a mixed $\s$-ideal of $R$. Further let $f \in R \setminus \a$. We set $$(\a:f):= \{ g \in R \mid gf \in \a \} \subseteq R$$
\end{defn}

\begin{lem}
Let $R$ be a $\s$-ring, $\a \si R$ a mixed $\s$-ideal, $f \notin \a$. Then $(\a:f)$ is a mixed $\s$-ideal of $R$ which contains $\a$. If $\a$ is radical/prime, then $(\a:f)$ is radical/prime as well.
\begin{bew}
Let $a,b \in (\a:f), r \in R$. Then $af, bf \in \a$ and thus $(a + b)f = af + bf \in \a$, which means that $a + b \in (\a:f)$. Similarly $$(ha)f = h\underbrace{(af)}_{\in \a} \in \a,$$
which means that $ha \in (\a:f)$. Also, since $\a$ is mixed and $af \in \a$ it follows that $\s(a)f \in \a$, which in turn means that $\s(a) \in (\a:f)$. We have shown that $(\a:f)$ is a difference ideal. 
That $\a \subseteq (\a:f)$ is an obvious conclusion from the fact that since $\a$ is an ideal, $fa' \in \a \fa a' \in \a$.  Finally, to see that $(\a:f)$ is mixed,
let $g,h \in R$ with $gh \in (\a:f)$. Then it holds that $(gh)f = (gf)h  \in \a$. Since $\a$ is mixed, this implies that $(gf)\s(h) = (g\s(h))f \in \a$, from which $g\s(h) \in (\a:f)$ follows immediately by definition. \\
\indent Assume now that $\a$ is radical, and let $g \in R$ such that $g^n \in (\a:f)$ for an $n \in \NE$. Then $g^nf \in \a$. This also implies (since $\a$ is an ideal), that $g^nf \cdot f^{n-1} = (gf)^n \in \a$.
Since $\a$ is radical, it follows from this that $gf \in \a$, and thus $g \in (a:f)$.\\ 
\indent Finally, assume that $\a$ is prime, and let $g, h \in R$ with $gh \in (\a:f)$. This means that $(gh)f = g(hf) \in \a$. Since $\a$ is prime, it has to hold that $g \in \a$ or $hf \in \a$. Since $\a \subseteq (\a:f)$, it follows that $g \in (\a:f)$ or $h \in (\a:f)$.
\end{bew}
\end{lem}

\begin{lem}\label{maxmixed=prime}
Let $R$ be a difference ring and let $\emptyset \neq U \subset R$ be a multiplicatively closed set of $R$. Then a mixed difference ideal $\a \subset R$ maximal (with respect to inclusion) in the class of mixed difference
ideals not meeting $U$, i.e. such that $\a \cap U = \emptyset$, is prime. 
\begin{bew}
Let $\a \subset R$ be a maximal mixed difference ideal not meeting $U$, and assume that $\a$ is not prime. Then there exist $f, g \in R$ such that $f,g \notin \a$ but $fg \in \a$.
We distinguish two cases: First, assume that there exists an $f \in U, g \in R$ with $fg \in \a$ and $f, g \notin \a$. Then $\a$ is a proper subset of the $\s$-ideal $(\a:f)$, since $g \in (\a:f)$ by definition, but by assumption $g \notin \a$.
Since $(\a:f)$ is mixed, by the maximality of $\a$, there exists an $u \in U \cap (\a:f)$. In particular, $uf \in \a$, but by assumption $f \in U$ and $U$ is multiplicatively closed, which implies that $fu \in U \cap \a$, a contradiction. \\
For the other case, assume that for all $f \in R \setminus \a$ for which there exists a $g \in R \setminus \a$ such that $fg \in \a$ it holds that $f \notin U$. Let $h \in R$ be such that this is the case, i.e., $h \in R \setminus \a$ and there exists a $g' \in R \setminus \a$ such that $g'h \in \a$.
By the same argument as above, $(\a:h) \supsetneqq \a$, which again implies that there exists an $u \in U \cap (\a:h)$. It holds by definition that $uh \in \a$. Nevertheless,  it holds that $u,h \notin \a$, which is a contradiction to the above assumption (with $f = u, g = h$) since $u \in U$. 
\end{bew}
\end{lem}

\begin{theorem}
Let $R$ be a differece ring and $F \subseteq R$ be a subset of $R$. Then
\[ \{ F \}_m = \bigcap_{F \subseteq \p \si R, \p \text{ prime }} \p.\]
\begin{proof}
The inclusion ``$\subseteq$'' is obvious, since prime difference ideals are mixed. For the inclusion ``$\supseteq$'', let $g \in R, ~ g \notin \{ F \}_m$, and consider the multiplicatively closed set $U = \{ g^k \mid k \in \NE \} \subset R$. 
$\{ F \}_m \cap U = \emptyset$ since $\{ F \}_m$ is radical. By Lemma \ref{maxmixed=prime}, any maximal mixed difference ideal $\p$ that is disjoint with $U$ is a prime difference ideal. We can always find a maximal mixed difference ideal over $\{F\}_m$ by Zorn's Lemma since
the union of any ascending chain of mixed difference ideals is always a mixed difference ideal. In particular, since $\{F\}_m$ is a mixed difference ideal disjoint from $U$, this implies that there exists a prime difference ideal $\p \supseteq \{F\}_m$ such that $g \notin \p$,
which in turn implies that $g \notin \bigcap_{\a \subseteq \p \si R, \p \text{ prime }} \p$. By taking the contraposition of this we get the desired inclusion.
\end{proof}
\end{theorem}
\end{document}
